---
title: "MOWNIT - Laboratorium 5"
output: html_notebook
---

Wojciech Klyszejko

```{r}
library("ggplot2");
```

Importing data from csv file
```{r}
data = read.csv("data_c.csv")
```

```{r}
head(data)
```


Change column name
```{r}
colnames(data)[2] = "type"
```

Change column type and values
```{r}
data$type = as.character(data$type)
data$type[data$type == "b"] <- "blas"
data$type[data$type == "n"] <- "naive"
data$type[data$type == "i"] <- "improved"
data$type = as.factor(data$type)
```

```{r}
head(data)
```

Group by length and operation type, add mean
```{r}
data_grouped = aggregate( time ~ length:type, data = data, FUN = mean)
```

Add standard deviation column
```{r}
data_grouped$std = aggregate( time ~ length:type, data = data, FUN = sd )$time
```

Plot results with error bars
```{r}
ggplot(data_grouped, aes(length,time)) + 
  geom_errorbar(aes(ymin=time - std, ymax=time + std)) + 
  geom_point(aes(color = type)) +
         labs(title ="Comparison between different types of square matrix multiplication" )
```

Aproximating naive algorithm by 3rd degree polynomial
```{r}
aprox_naive = data_grouped[data_grouped$type == "naive",]
```

```{r}
fit_naive = lm(time ~ poly(length, 3, raw=TRUE), data=aprox_naive)
fit_naive
```

```{r}
ggplot(aprox_naive,aes(length,time)) + geom_point(color = "red") +
         labs(title ="Naive matrix multiplication")
```

```{r}
points_naive = data.frame(length = seq(0,1000, length.out=250))
```

```{r}
points_naive$time = predict(fit_naive, points_naive)
last_plot() + geom_line(data=points_naive, aes(length,time), color = "blue")+
         labs(title ="Aproximating naive matrix multiplication with a 3rd degree polynomial")
```

Aproximating improved algorithm by 3rd degree polynomial
```{r}
aprox_improved = data_grouped[data_grouped$type == "improved",]
```

```{r}
fit_improved = lm(time ~ poly(length, 3, raw=TRUE), data=aprox_improved)
fit_improved
```

```{r}
ggplot(aprox_improved,aes(length,time)) + geom_point(color = "red") +
         labs(title ="Improved matrix multiplication")
```

```{r}
points_improved = data.frame(length = seq(0,1000, length.out=250))
```

```{r}
points_improved$time = predict(fit_improved, points_improved)
last_plot() + geom_line(data=points_improved, aes(length,time), color = "blue")+
         labs(title ="Aproximating improved matrix multiplication with a 3rd degree polynomial")
```

Aproximating BLAS algorithm by 2nd degree polynomial
```{r}
aprox_blas = data_grouped[data_grouped$type == "blas",]
```

```{r}
fit_blas = lm(time ~ poly(length, 2, raw=TRUE), data=aprox_blas)
fit_blas
```

```{r}
ggplot(aprox_blas,aes(length,time)) + geom_point(color = "red") +
         labs(title ="BLAS matrix multiplication")
```

```{r}
points_blas = data.frame(length = seq(0,1000, length.out=250))
```

```{r}
points_blas$time = predict(fit_blas, points_blas)
last_plot() + 
  geom_line(data=points_blas, aes(length,time), color = "blue") +
         labs(title ="Aproximating BLAS matrix multiplication with a 2nd degree polynomial")
```